### 2014-02-26 paper/Rcode/ashsim.rmd
updated mix.R to export loglik_conv.default

```{r}
pdf("figures/simABC_egdens.pdf",width=6.5,height=2)
plot_examples(list(simA,simB,simC))
dev.off()
```

```{r}
  pdf("figures/rmse_biplot.pdf",width=6.5,height=2)
    plot_rmse(list(simA,simB,simC))
  dev.off()

#This figure not used in paper?
pdf("figures/rmse_biplot_withzerobetahat.pdf")
    plot_rmse(list(simA,simB,simC),inczero=TRUE,incbetahat=TRUE)
dev.off()

```

```{r}

  pdf("figures/rmse_boxplot.pdf",width=6.5,height=2)
    plot_rmse_boxplot(list(simA,simB,simC))
  dev.off()

    pdf("figures/rmse_boxplot_extended.pdf",width=6.5,height=2)
    plot_rmse_boxplot(list(simA,simB,simC),TRUE,TRUE,TRUE)
  dev.off()

```

```{r}

  pdf("figures/loglik_boxplot.pdf",width=6.5,height=2)
    plot_loglik_boxplot(list(simA,simB,simC))
  dev.off()

```

```{r}

  pdf("figures/rmse_loglik_boxplot.pdf",width=6.5,height=5)
    plot_rmse_loglik_boxplot(list(simA,simB,simC))
  dev.off()

```

@@

```{r}
temp=mixFdr(simC$betahat[[1]]/simC$betahatsd[[1]],noiseSD=1,theonull=TRUE,calibrate=TRUE)
temp2=mixFdr(simC$betahat[[1]]/simC$betahatsd[[1]],noiseSD=1,theonull=TRUE,J=10,plot=FALSE)
plot(ecdf(simC$beta[[1]]),xlim=c(-6,6))
lines(x,cdf.mixfdr(temp,x),col=3)
lines(cdf.ash(simC$fit.ash.n[[1]],x),col=2)
lines(cdf.ash(simC$fit.ash.hu[[1]],x),col=2,lty=2)
```

```{r}
  plot_LR=function(sims){
    hist(unlist(lapply(sims$fit.ash.u,get_loglik))-unlist(lapply(sims$fit.ash.n,get_loglik)), xlab="loglik difference", main="loglik differences for nullbiased prior vs mle",nclass=10)
  }

  pdf("figures/logLR.pdf")
    plot_LR(simA)
    plot_LR(simB)
  dev.off()
```

## Unused figures?

```{r}

pdf("figures/simABC_eg_withfit.pdf",width=6.5,height=2)
plot_examples_withfit(list(simA,simB,simC))
dev.off()
```

```{r}
pdf("figures/simABC_eg_cdf_withfit.pdf",width=6.5,height=2)
plot_examples_cdf_withfit(list(simA,simB,simC))
dev.off()
```

@@

pdf("figures/penaltycompare.pdf")
ggplot(res.melt, aes(x=beta)) +
  geom_line(aes(x=beta,y=value,color=Methodtype,linetype=Penalization,group=Method),size=1.5,alpha=0.8) +
  geom_line(data=res, aes(y=truth,color="truth"),alpha=1,size=0.5) +
  scale_colour_manual(name = 'Method', values = cbbPalette)
dev.off()
```

>>>>

@@

```{r}
temp=mixFdr(simC$betahat[[1]]/simC$betahatsd[[1]],noiseSD=1,theonull=TRUE,calibrate=TRUE)
temp2=mixFdr(simC$betahat[[1]]/simC$betahatsd[[1]],noiseSD=1,theonull=TRUE,J=10,plot=FALSE)
plot(ecdf(simC$beta[[1]]),xlim=c(-6,6))
x= seq(-6,6,length=100)
lines(x,cdf.mixfdr(temp,x),col=3)
lines(cdf.ash(simC$fit.ash.n[[1]],x),col=2)
lines(cdf.ash(simC$fit.ash.hu[[1]],x),col=2,lty=2)
```

@@

#pdf("figures/penaltycompare.pdf")
ggplot(res.melt, aes(x=beta)) +
  geom_line(aes(x=beta,y=value,color=Methodtype,linetype=Penalization,group=Method),size=1.5,alpha=0.8) +
  geom_line(data=res, aes(y=truth,color="truth"),alpha=1,size=0.5) +
  scale_colour_manual(name = 'Method', values = cbbPalette)
#dev.off()
```
